---
title: 'Violence: The Role of Disadvantage by Climate Zone'
author: 'Erin M. Ochoa'
date: '2018/05/18'
class: 'Data Visualization'
professor: 'Dr. Soltoff'
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: spacelab
---

```{r setup}
library(sp)
library(rgdal)
library(leaflet)
library(htmltools)
library(RColorBrewer)
```

```{r read_data, message=FALSE, warning=FALSE,echo=FALSE,include=FALSE}
zones <- readOGR('data/climatezones_aug.shp',layer='climatezones_aug', GDAL1_integer64_policy = TRUE)
```


```{r prepare_components}
m0.bins = c(-Inf,-6.0,-1.5,-.0001,0.0001,1.5,6.0,Inf)
m0.pal <- colorBin('RdBu', domain = zones$Coef0Z, bins = m0.bins, reverse=TRUE)

m3.bins = c(-Inf,-.812,-.527,0,0.0001,.326,.611,Inf)
m3.pal <- colorBin('RdBu', domain = zones$Coef3Z, bins = m3.bins, reverse=TRUE)

m4.bins.zone = c(-Inf,-.640,-.228,-.038,0.0001,.236,.646,Inf)
m4.pal.zone <- colorBin('RdBu', domain = zones$Coef4Z, bins = m4.bins.zone, reverse=TRUE)

m4.bins.int = c(-Inf,-.236,-.059,0,0.001,0.3,0.620,Inf)
m4.pal.int <- colorBin('RdBu', domain = zones$Coef4Int, bins = m4.bins.int, reverse=TRUE)
  
m5.bins <- seq(min(zones$Coef5D),max(zones$Coef5D),by=(max(zones$Coef5D) - min(zones$Coef5D))/7)
m5.pal <- colorBin('YlOrRd', domain = zones$Coef5D, bins = m5.bins, reverse=TRUE)

m6.bins <- seq(min(zones$Coef6D),max(zones$Coef6D),by=(max(zones$Coef6D) - min(zones$Coef6D))/7)
m6.pal <- colorBin('YlOrRd', domain = zones$Coef6D, bins = m6.bins, reverse=TRUE)

m7.bins <- seq(min(zones$Coef7D),max(zones$Coef7D),by=(max(zones$Coef7D) - min(zones$Coef7D))/7)
m7.pal <- colorBin('YlOrRd', domain = zones$Coef7D, bins = m7.bins, reverse=TRUE)

base.labels <- sprintf(
  "<strong>%s</strong><br/>",
  zones$Name
) %>% lapply(HTML)

m0.labels <- sprintf(
  "<strong>%s</strong><br/>Base Model Coefficient:  %g",
  zones$Name, zones$Coef0Z
) %>% lapply(HTML)

m3.labels <- sprintf(
  "<strong>%s</strong><br/>Model 3 Zone Coefficient:  %g",
  zones$Name, zones$Coef3Z
) %>% lapply(HTML)

m4.labels <- sprintf(
  "<strong>%s</strong><br/>Model 4 Zone Coefficient:  %g",
  zones$Name, zones$Coef4Z
) %>% lapply(HTML)

m4.int.labels <- sprintf(
  "<strong>%s</strong><br/>Model 4 Zone x Disadvantage Coefficient:  %g",
  zones$Name, zones$Coef4Int
) %>% lapply(HTML)

m5.labels <- sprintf(
  "<strong>%s</strong><br/>Model 5 (OLS by Regimes) Disadvantage Coefficient:  %g",
  zones$Name, zones$Coef5D
) %>% lapply(HTML)

m6.labels <- sprintf(
  "<strong>%s</strong><br/>Model 6 (Spatial Lag by Regimes) Disadvantage Coefficient:  %g",
  zones$Name, zones$Coef6D
) %>% lapply(HTML)

m7.labels <- sprintf(
  "<strong>%s</strong><br/>Model 7 (Spatial Error by Regimes) Disadvantage Coefficient:  %g",
  zones$Name, zones$Coef7D
) %>% lapply(HTML)

hopts <- highlightOptions(weight = 4,
                       color = "#555555",
                       dashArray = "",
                       fillOpacity = .6,
                       bringToFront = TRUE)

lopts <- labelOptions(style = list("font-weight" = "normal"),
                      textsize = "15px",direction = "auto",opacity=1)

zones.map <- leaflet(zones,option=leafletOptions(zoomControl=FALSE,minZoom=4, maxZoom=4)) %>%
               addProviderTiles(providers$CartoDB.PositronNoLabels) %>%
               addLabelOnlyMarkers(lng = ~Lon, lat = ~Lat, label = ~as.character(zone),
                                     labelOptions = labelOptions(noHide = TRUE, direction = 'top', textOnly = TRUE,
                                                  style = list("font-size" = "14px")))
```

### Introduction {data-commentary-width=400}

```{r frame1}

```

*** 

<b>Intro text goes here.</b><br>  Figure should be the homicide-rate-by-county map.

### Climate Regions {data-commentary-width=400}

```{r frame2}
zones.map %>% addPolygons(weight = 1, color = '#000000',opacity = 1.0,fill=TRUE,fillOpacity = 0.6, fillColor = ~Color,
                                                               highlight = hopts,
                                                               label = base.labels,
                                                               labelOptions = lopts)
```

*** 

Map of the fourteen climate zones in which there are observations.

### Raw Violence Rates {data-commentary-width=400}

```{r frame3}
zones.map %>% addPolygons(weight = 1, color = '#000000',opacity = 1.0,fill=TRUE,fillOpacity = 0.6, fillColor = ~m0.pal(zones$Coef0Z),
                                                                highlight = hopts,
                                                                label = m0.labels,
                                                                labelOptions = lopts) %>%
                                                addLegend(pal=m0.pal, values=~zones$Coef0Z, opacity = 0.7, title = NULL,position='bottomright')
```

*** 

text

### Model A: Climate Zone {data-commentary-width=400}

```{r frame4}
zones.map %>% addPolygons(weight = 1, color = '#000000',opacity = 1.0,fill=TRUE,fillOpacity = 0.6, fillColor = ~m3.pal(zones$Coef3Z),
                                                            highlight = hopts,
                                                            label = m3.labels,
                                                            labelOptions = lopts) %>%
                                                addLegend(pal=m3.pal, values=~zones$Coef3Z, opacity = 0.7, title = NULL,position='bottomright')
```

*** 

Text

### Model B: Climate Zone (when Disadvantage  = 0) {data-commentary-width=400}

```{r frame5}
zones.map %>% addPolygons(weight = 1, color = '#000000',opacity = 1.0,fill=TRUE,fillOpacity = 0.6,
                                                            fillColor = ~m4.pal.zone(zones$Coef4Z),
                                                            highlight = hopts,
                                                            label = m4.labels,
                                                            labelOptions = lopts) %>%
                                                addLegend(pal=m4.pal.zone, values=~zones$Coef4Z, opacity = 0.7, title = NULL,position='bottomright')
```

*** 

Text

### Model B: Climate Zone x Disadvantage {data-commentary-width=400}

```{r frame6}
zones.map %>% addPolygons(weight = 1, color = '#000000',opacity = 1.0,fill=TRUE,fillOpacity = 0.6,
                                                                fillColor = ~m4.pal.int(zones$Coef4Int),
                                                                highlight = hopts,
                                                                label = m4.int.labels,
                                                                labelOptions = lopts) %>%
                                                    addLegend(pal=m4.pal.int, values=~zones$Coef4Int, opacity = 0.7, title = NULL,position='bottomright')
```

*** 

Text

### Model C: OLS by Climate Regions (Disadvantage) {data-commentary-width=400}

```{r frame7}
zones.map %>% addPolygons(weight = 1, color = '#000000',opacity = 1.0,fill=TRUE,fillOpacity = 0.6,
                                                            fillColor = ~m5.pal(zones$Coef5D),
                                                            highlight = hopts,
                                                            label = m5.labels,
                                                            labelOptions = lopts) %>%
                                                addLegend(pal=m5.pal, values=~zones$Coef5D, opacity = 0.7, title = NULL,position='bottomright')
```

*** 

Text

### Model D: Spatial Lag by Regions (Disadvantage) {data-commentary-width=400}

```{r frame8}
zones.map %>% addPolygons(weight = 1, color = '#000000',opacity = 1.0,fill=TRUE,fillOpacity = 0.6,
                                                            fillColor = ~m6.pal(zones$Coef6D),
                                                            highlight = hopts,
                                                            label = m6.labels,
                                                            labelOptions = lopts) %>%
                                                addLegend(pal=m6.pal, values=~zones$Coef6D, opacity = 0.7, title = NULL,position='bottomright')
```

*** 

Text

### Model E: Spatial Error by Regions (Disadvantage) {data-commentary-width=400}

```{r frame9}
zones.map %>% addPolygons(weight = 1, color = '#000000',opacity = 1.0,fill=TRUE,fillOpacity = 0.6,
                                                            fillColor = ~m7.pal(zones$Coef7D),
                                                            highlight = hopts,
                                                            label = m7.labels,
                                                            labelOptions = lopts) %>%
                                                addLegend(pal=m7.pal, values=~zones$Coef7D, opacity = 0.7, title = NULL,position='bottomright')
```

*** 

Text